network_plot_work

### 2024-01-11 R/Paper_markdown.Rmd
24_11_01_1

#bibliography: "`r rbbt::bbt_write_bib('MASCARA_refs.json', overwrite = TRUE, filter = ("accessed"))`"

@@

```{r , echo=FALSE, include=FALSE}
#SOURCE FUNCTIONS FROM EXTERNAL FILE
source("DATA_SIM_FUNCS.R")
```

@@

```{r}
# renv::snapshot()  #change this

@@

```{r, echo = F}
META <- META[!duplicated(paste0(META$growth_condition, META$time)),]
rownames(META) <- NULL
# kable(META, format = "simple") #replace with CANDTAB like

@@

# rdo <- list(META,rdo[[1]],rdo[[2]],rdo[[3]])
# plot_grid(META)
# # grid.newpage()
# # grid.draw(META)
```

```{r, echo = F}
# h <- readRDS("heat_comp.RDS")
# levels(h[[2]]$time) <- c("1","3","7","8")
# 
# ann_colours <- list(g_c = c("P-" = "#F8766D","P+" = "lightblue"),
#                     time = c("1" = "#fde725","3" = "#35b779","7" = "#31688e","8" = "#440154"))
# 
# heat <- pheatmap::pheatmap(t(scale(t(h[[1]]))),  #
#                              cluster_rows = T,
#                              cluster_cols = F, 
#                              show_rownames = T, 
#                              show_colnames = F,
#                              annotation_col = h[[2]],
#                            annotation_colors = ann_colours,
#                            treeheight_row = 10,
#                            fontsize = 8,
#                              # annotation_row = anno,
#                              main = "Strigolactone Gene Expression",silent = T)
#   
#   # heat
#   library(ggplotify)
#   heat2 <- as.ggplot(heat) + theme(plot.title = element_text(face = "plain"))

# heat2 <- readRDS("heatmap_MASCARA_Fig_2.RDS")

@@

```{r ASCA-1, echo = F, out.width = '100%', fig.cap=c("Scores and loadings of the ASCA model of the combined effect (condition + condition:time interaction), model indicates samples and genes relative positions in the designed variance. *g_c* indicates growth condition, *time* indicates days after starvation induction.")}
knitr::include_graphics("rice_s_l.png")

@@

<!-- The simulated data is created by simulating score and loading values (as in Figure \@ref(fig:simOverview)) for the combined effect ($\alpha + \alpha\beta$) ) explaining the difference in time profiles of the P+ and P- condition and the main time effect $\beta$, as well as, structured ambient variance ($S$). This is to mimic variance due to gene expression as a function of growth condition and time as well as variance due to coexpression of genes in the same  pathway on top of this experimentally induced DE variance. -->

@@

<!-- For example the correlation between a SL gene $j_{sl}$ and a non-SL gene $j_q$ is calculated as: -->

<!-- \begin{equation} -->
<!-- \begin{aligned} -->
<!--   r_{j_{sl}j_{q}} = \frac{\sum_{i=1}^{I} (y_{ij_{sl}} - \bar{y}_j_{sl}) (y_{ij_{q}} - \bar{y}_j_{q})}{\sqrt{\sum_{i=1}^{I} (y_{ij_{sl}} - \bar{y}_j_{sl})^2 \sum_{i=1}^{I} (y_{ij_{q}} - \bar{y}_j_{q})^2}} -->
<!-- \end{aligned}(\#eq:Pearson) -->
<!-- \end{equation} -->

@@

<!-- The MASCARA pipeline in exemplified in Figure \@ref(fig:MASCARAOVERVIEW). -->

<!-- ```{r MASCARAOVERVIEW, echo = F, fig.cap="MASCARA pipeline overview"} -->
<!-- a <- knitr::include_graphics("MASCARA_Pipeline_overview.png") -->
<!-- a -->
<!-- ``` -->

@@

  #this predict method does matrix multiplication of the input (new data) and the rotation (loading) matrix
  #projects the data into the PCA space
  PCDE <- predict(PCD, newdata)
  # PCDE <- cbind(m[,1:2], PCDE)

@@

```{r, echo = F}
a_c.PCD <- PCD

@@

# f <- F1_plot(ASCA_cands, baits, 500)[[2]]
```

@@

# #remove RP samples
# X <- X[-which(meta$growth_condition == "PR"),]
# meta <- meta[-which(meta$growth_condition == "PR"),]
# 
meta$time <- as.character(meta$time)

@@

# REF <- readRDS("ref4ASCA_rice.RDS")
ref <- cbind.data.frame(Feature = colnames(X), feature = colnames(X), Baits = colnames(X))

@@

# baits <- SL_ref$feature

@@

```{r extra plot making}
# ASCA_cands3 <- ASCA_cands2[-which(rownames(ASCA_cands2) %in% c("Os06t0570600-00","Os06t0570566-00", "Os09t0321200-00","Os06t0651900-01", "Os10t0444566-00")),]
# h <- readRDS("heat_comp.RDS")
# levels(h[[2]]$time) <- c("1","3","7","8")
# 
# # make row annotation
# 
# row_ann <- data.frame("Feature" = rep(c("SL","Other DE"),each = 9))
# rownames(row_ann) <- c(pathway,rownames(ASCA_cands3)[1:9])
# 
# ann_colours <- list(g_c = c("P-" = "#F8766D","P+" = "lightblue"),
#                     time = c("1" = "#fde725","3" = "#35b779","7" = "#31688e","8" = "#440154"),
#                     Feature = c("SL" = "purple", "Other DE" = "lightgreen"))
# 
# h[[1]] <- t(X[,c(pathway,rownames(ASCA_cands3)[1:9])])  #psi_ref[,1]
# 
# heat <- pheatmap::pheatmap(t(scale(t(h[[1]]))),  #
#                              cluster_rows = F,
#                              cluster_cols = F,
#                              show_rownames = T,
#                              show_colnames = F,
#                              annotation_col = h[[2]],
#                            annotation_row = row_ann,
#                            annotation_colors = ann_colours,
#                            treeheight_row = 10,
#                            fontsize = 8,
#                              # annotation_row = anno,
#                              main = "Scaled Gene Expression",silent = T)
# 
#   # heat
#   library(ggplotify)
#   heat2 <- as.ggplot(heat) + theme(plot.title = element_text(face = "plain"))
#
#   saveRDS(heat2, "heatmap_MASCARA_Fig_2.RDS")

# 
# qqplot <- function(data, meta, ...){
# 
#   df <- cbind.data.frame(meta,data)
# 
#   df$time <- factor(df$time, levels = unique(meta$time))
#   df$growth_condition <- factor(df$growth_condition)
# 
# 
#   ggplot(df, ...) +
#     geom_point() +
#     theme_bw()
# 
# 
# }
# 
# meta$time <- rep(c(1,3,7,8), each = 3, 2)
# 
# cand_b <- PSI_cands[10]
# cand_w <- baits[3]
# 
# cor_tw <- round(cor(X[,which(colnames(X) %in% cand_w)], X[,which(colnames(X) %in% baits[4])]), digits = 2)
# 
# cor_tb <- round(cor(X[,which(colnames(X) %in% cand_b)], X[,which(colnames(X) %in% baits[4])]), digits = 2)
# 
# cor_rw <- round(cor(res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% cand_w)], res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% baits[4])]), digits = 2)
# 
# cor_rb <- round(cor(res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% cand_b)], res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% baits[4])]), digits = 2)
# 
# 
# within <- qqplot(cbind.data.frame("Candidate" = X[,which(colnames(X) %in% cand_w)],
#                         "Bait" = X[,which(colnames(X) %in% baits[4])]),meta,
#        aes(x = Bait, y = Candidate, colour = growth_condition, shape = time)) + xlab(baits[4]) + ylab(cand_w) + labs(title = paste0("r = ",cor_tw))
# 
# PSI_cands <- rownames(ASCA_cands[which(rownames(ASCA_cands) %in% psi_ref[,1]),])
# PSI_cands <- head(rownames(ASCA_cands[-which(rownames(ASCA_cands) %in% pathway),]),20)
# 
# 
# between <- qqplot(cbind.data.frame("Candidate" = X[,which(colnames(X) %in% cand_b)],
#                         "Bait" = X[,which(colnames(X) %in% baits[4])]),meta,
#        aes(x = Bait, y = Candidate, colour = growth_condition, shape = time)) + xlab(baits[4]) + ylab(cand_b) + labs(title = paste0("r = ",cor_tb))
# 
# # within + between + plot_layout(guides = "collect",tag_level = 'new') + plot_annotation(tag_levels = c('A')) + plot_layout(heights = unit(c(5), c("cm")), widths = c(5))
# 
# 
# 
# 
# within_r <- qqplot(cbind.data.frame("Candidate" = res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% cand_w)],
#                         "Bait" = res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% baits[4])]),meta,
#        aes(x = Bait, y = Candidate, colour = growth_condition, shape = time)) + xlab(baits[4]) + ylab(cand_w)   + labs(title = paste0("r = ",cor_rw))#, alpha = (16- as.numeric(growth_condition))
# 
# 
# between_r <- qqplot(cbind.data.frame("Candidate" = res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% cand_b)],
#                         "Bait" = res_ASCAplus_nb$residuals[,which(colnames(res_ASCAplus_nb$residuals) %in% baits[4])]),meta,
#        aes(x = Bait, y = Candidate, colour = growth_condition, shape = time)) + xlab(baits[4]) + ylab(cand_b)  + labs(title = paste0("r = ",cor_rb))
# 
# (within + between)/(within_r + between_r) + plot_layout(guides = "collect",tag_level = 'new') + plot_annotation(tag_levels = c('A','1')) #+ plot_layout(heights = unit(c(5), c("cm")), widths = c(5))

#^^ C:/Users/fwhite/Documents/within_between_example_2.png
```

>>>>

#bibliography: "`r rbbt::bbt_write_bib('MASCARA_refs.json', overwrite = TRUE)`"

@@

```{r , echo=FALSE, include=FALSE}
source("DATA_SIM_FUNCS.R")
```

@@

@@

```{r, echo = F}
META <- META[!duplicated(paste0(META$growth_condition, META$time)),]
rownames(META) <- NULL

@@

@@

```{r ASCA-1, echo = F, out.width = '100%', fig.cap=c("Scores and loadings of the ASCA model of the combined effect (condition + condition:time interaction), model indicates samples and genes relative positions in the designed variance. *g_c* indicates growth condition, *time* indicates days after starvation induction.")}
knitr::include_graphics("rice_s_l.png")
```

@@

@@

@@

@@

  PCDE <- predict(PCD, newdata)
  # PCDE <- cbind(m[,1:2], PCDE)

@@

```{r, echo = F}
a_c.PCD <- PCD
```

@@

@@

meta$time <- as.character(meta$time)

@@

ref <- cbind.data.frame(Feature = colnames(X), feature = colnames(X), Baits = colnames(X))

@@

@@

### 2024-01-11 R/run_first/2.plot_pathway_net_example.Rmd
24_11_01_1

```{r}
library(ggrepel)
library(readxl)
library(extrafont)
library(cowplot)
library(graphlayouts)
library(gganimate)
library(animation)
```

```{r}
# font_import() # download once 
#windowsFonts() # to check which are loaded
```

@@

#
# plot residuals and full (with tweaks for problem demonstration)

@@

@@

cand_vals <- residuals[,1970:2000]    #rgs[which(rownames(rgs) %in% names(g_b)[1:50]),]

>>>>

```{r}
library(ggrepel)
library(readxl)
library(extrafont)
library(cowplot)
library(graphlayouts)
library(gganimate)
library(animation)
library(gASCA)
library(matrixStats)
library(patchwork)

source("../DATA_SIM_FUNCS.R")
```

```{r}
# font_import() # download once 
#windowsFonts() # to check which are loaded

renv::status()

@@

#
# plot residuals and full (with tweaks for problem demonstration)
baits <- paste0("X_",c(1985:1988))   #501:510
spikes <- paste0("X_",c(1989:2000))

@@

meta <- cbind.data.frame(rep(c(1,-1), each = 12), rep(c(1:4), each = 3), rep(c(-1:-4,1:4), each = 3))
colnames(meta) <- c("growth_condition","time","interaction")
meta <- as.data.frame(apply(meta,2,factor))  #9

Experiment_responders <- 30

sim_data <- Create_Core_DEV_2(nreps = 3, meta = meta, 
                        EffectSize = c(X_a_ab = 5, time = 1, E = 1, mu = 1, Struc_E = 0.4),    # E = 10, Struc_E = 1
                        struc_resid = TRUE, e_sigma = c(1.5,0.8,0.0), a_sigma = c(1,0.7,0.6,0.1),
                        b_sigma = c(1,0.9), irr_spikes = TRUE, SCORE_SEED = 12, Experiment_responders = Experiment_responders,
                        struc_seed = 127, score_plot = FALSE, plot = FALSE)  #12

ar <- ASCA(sim_data[[1]], m = meta, Baits = baits, spikes = spikes, ncands = ncands, distance_calc = FALSE, Return_Model = FALSE)

@@

cand_vals <- residuals[,1970:2000]    #rgs[which(rownames(rgs) %in% names(g_b)[1:50]),]
adj <- cor(cand_vals)
